Log or not - Analysis of ECDC forecasts

### 2021-10-26 analysis/Analysis ECDC forecasts.Rmd
show regresssion code in markdown file

```{r include=TRUE}
reg_log <- scores |>
  filter(scale == "log") |>
  glm(formula = interval_score ~ 1 + model + location + target_type + horizon, 
      family = gaussian)

reg <- scores |>
  filter(scale == "natural") |>
  glm(formula = interval_score ~ 1 + model + location + target_type + horizon, 
      family = gaussian)
```

>>>>

Check fit of the log scale model

```{r echo=TRUE}
reg_log <- scores |>
  filter(scale == "log") |>
  glm(formula = interval_score ~ 1 + model + location + target_type + horizon, 
      family = gaussian)
```
